A geometric approach to linear and quadratic Chabauty

### 2020-02-12 MS.tex
Worked on deg exp_p mod p^m

As $c_n$ has $p$-adic valuation $n-1$ for $...$
\end{proof}
[TODO: I'd like to study what happens modulo higher powers of $p$; for example, if $\log_p$ is at most quadratic mod $p^2$, then so is $\exp_p$; and similar for $\log_p$ at most cubic mod $p^3$. Even in general, if $\log_p$ has degree at most $d$ modulo $p^k$, then $\exp_p$ has degree at most $f = f(d,k)$ (seen most easily by working in a ``universal'' ring $\Z[p]/(p^k)$).

>>>>

Finally, let $m \in \Z_{>0}$ with $p > m+1$. As $c_n$ has $p$-adic valuation $n-1$ for $n < p$, and $p$-adic valuation at least $p-2 \geq m$ for $n \geq p$, indeed $\log_p$ has degree at most $m$ modulo $p^m$. Then the statement that $\exp_p$ has degree at most $m$ modulo $p^m$ is easily proven by the formula in $\Z/p^m\Z[x,\varepsilon]$ that $\log_p(g(x) -\varepsilon)+\varepsilon$
\end{proof}
[TODO: I'd like to study what happens modulo higher powers of $p$; for example, if $\log_p$ is at most quadratic mod $p^2$, then so is $\exp_p$; and similar for $\log_p$ at most cubic mod $p^3$. Even in general, if $\log_p$ has degree at most $d$ modulo $p^k$, then $\exp_p$ has degree at most $f = f(d,k)$ (seen most easily by working in a ``universal'' ring $\Z[p]/(p^k)$).
